Insert the article title here

### 2018-04-04 writeup/manuscript.tex
small edit

%%%%%%%%% Insert author address here
\address{
$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State Universoty, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
}

@@

>>>>

%%%%%%%%% Insert author address here
\address{$^{1}$Department of Psychology, University of Essex, Colchester, UK\\
$^{2}$Department of Psychology, The Ohio State Universoty, Columbus, USA\\
$^{3}$School of Psychology, University of Aberdeen, Aberdeen, UK
}

@@

The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms. Are observers who are good at finding the target in the split-half search arrays also better in the ACVS task? Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms? As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.
